Results

### 2024-10-11 scripts/Results.Rmd
check landscape metrics again

# rm(fp, fp_2, fp_5, fp_8, labs, prctn, sm50, sm80, linecols)
```

@@

4) What is the relationship between patch metrics and population size? 
```{r}

scout_long <- pivot_longer(scouting, cai:enn_mn)

ggplot(scout_long, aes(y = POPULATION_SIZE, x = value)) +
  geom_point() +
  facet_grid(. ~ name)

>>>>

rm(fp, fp_2, fp_5, fp_8, labs, prctn, sm50, sm80, linecols)
```

@@

4) What is the relationship between patch metrics and population size? 
```{r}
write.csv(scout_long, '../data/SOS/LandscapeMetrics.csv')

scout_long <- pivot_longer(scouting, cai:enn_mn)
scout_long <- mutate(
  scout_long, 
  POP_CENSUS_SQRT = sqrt(POPULATION_SIZE),
  POP_CENSUS_LOG = log(POPULATION_SIZE)
  )

write.csv(scout_long, '../data/SOS/LandscapeMetrics.csv')

ggplot(scout_long, aes(y = POP_CENSUS_LOG, x = value)) +
  geom_point() +
  facet_grid(. ~ name, scales = 'free') +
  geom_smooth(aes(group=name))

scout_long
